FictionEro2 - Determinants of Reality Beliefs

### 2025-05-27 study2/analysis/2_emotion.qmd
updated scripts/analysis

stars2 <- data.frame(label=c("**", "*"),
                    Gender=fct_relevel(c("Male", "Male")),
                    Type=c("All trials", "'AI was more attractive'"),
                    y=c(0.52, 0.65))

>>>>

stars2 <- data.frame(label=c("**", "***", "*"),
                    Gender=fct_relevel(c("Male", "Male", "Male")),
                    Type=c("All trials", "Believed trials" ,"'AI was more attractive'"),
                    y=c(0.52, 0.56, 0.66))

### 2025-05-27 study2/analysis/3_realness.qmd
updated scripts/analysis

stars2 <- data.frame(Gender = as.factor(c("Male")),
                     feedback = as.factor("Feedback_AILessArousing"),
                    label=c("***"),
                    x=c(1.03),
                    y=c(0.58))
# stars3 <- data.frame(Sex = as.factor(c("Male", "Male", "Female")), 
#                      label=c("***", "***", "***"),
#                      x=c(1.1, 1.8, 1.15),
#                      y=c(0.71, 0.80, 0.615))

@@

p1 <- pred1 |> 
  ggplot(aes(x=Feedback_AILessArousing, y=Predicted)) +
  geom_line(aes(color=Condition, group=Condition), linewidth=.3, position = position_dodge(width=0.2), key_glyph = "path") +
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.2), size=0.8, linewidth=1, key_glyph = "blank") +
  # geom_text(data=stars2, aes(x=x, y=y, label=label, color=Condition), hjust=0.5, key_glyph = "blank", size=3) +
  geom_text(data=stars2, aes(x=x, y=y, label=label), hjust=0.5, color="#424242", size=3) +
  guides(color=guide_legend(override.aes = list(linewidth = 1.5))) +
  facet_grid(~Gender) +
  scale_y_continuous(labels=scales::percent) +
  scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 8),
        strip.placement = "outside",
        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
        strip.text.x = element_text(size = 10),
        strip.text.y = element_text(size = 10),
        axis.text.x = element_text(size=9, color="black"),
        legend.text = element_text(size = 10)) +
  labs(y="Realness\n", fill="Images presented as:", color="Images presented as:",
       x = "\n'AI-Images were less arousing' Feedback",
       tag = "B")

@@

# stars2 <- data.frame(
#   Gender = as.factor("Male"),
#   Condition = "AI-Generated",
#   label = "***",
#   x = 1.5,
#   y = 0.5)

@@

p2 <- pred2 |> 
  ggplot(aes(x=Feedback_NoFacesAttractive, y=Predicted)) +
  geom_line(aes(color=Condition, group=Condition), linewidth=.3, position = position_dodge(width=0.2), key_glyph = "path") +
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.2), size=0.8, linewidth=1, key_glyph = "blank") +
  # geom_text(data=stars2, aes(x=x, y=y, label=label, color=Condition), hjust=0.5, key_glyph = "blank", size=3) +
  # geom_text(data=stars2, aes(x=x, y=y, label=label), hjust=0.5, color="#424242", size=3) +
  guides(color=guide_legend(override.aes = list(linewidth = 1.5))) +
  facet_grid(~Gender) +
  scale_y_continuous(labels=scales::percent) +
  scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 8),
        strip.placement = "outside",
        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
        strip.text.x = element_text(size = 10),
        strip.text.y = element_text(size = 10),
        axis.text.x = element_text(size=9, color="black"),
        legend.text = element_text(size = 10)) +
  labs(y="Realness\n", fill="Images presented as:", color="Images presented as:",
       x = "\n'AI-Faces were less attractive' Feedback",
       tag = "B")

@@

>>>>

stars2 <- data.frame(Gender = as.factor(c("Male")),
                     feedback = as.factor("Feedback_AILessArousing"),
                    label=c("***"),
                    x=c(1.0),
                    y=c(0.545))
# stars3 <- data.frame(Sex = as.factor(c("Male", "Male", "Female")), 
#                      label=c("***", "***", "***"),
#                      x=c(1.1, 1.8, 1.15),
#                      y=c(0.71, 0.80, 0.615))

@@

p1 <- pred1 |> 
  ggplot(aes(x=Feedback_AILessArousing, y=Predicted)) +
  geom_line(aes(color=Condition, group=Condition), linewidth=.3, position = position_dodge(width=0.3), key_glyph = "path") +
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.3), size=0.8, linewidth=1, key_glyph = "blank") +
  # geom_text(data=stars2, aes(x=x, y=y, label=label, color=Condition), hjust=0.5, key_glyph = "blank", size=3) +
  geom_text(data=stars2, aes(x=x, y=y, label=label), hjust=0.5, color="#424242", size=3) +
  guides(color=guide_legend(override.aes = list(linewidth = 1.5))) +
  facet_grid(~Gender) +
  scale_y_continuous(labels=scales::percent) +
  scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 8),
        strip.placement = "outside",
        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
        strip.text.x = element_text(size = 10),
        strip.text.y = element_text(size = 10),
        axis.text.x = element_text(size=9, color="black"),
        legend.text = element_text(size = 10)) +
  labs(y="Realness\n", fill="Images presented as:", color="Images presented as:",
       x = "\n'AI-Images were less arousing' Feedback",
       tag = "A")

@@

stars3 <- data.frame(Gender = as.factor(c("Female", "Female")), 
                    Condition=c("Photograph", "AI-Generated"), 
                    label=c("**", "**"),
                    x=c(1.3, 1.7),
                    y=c(0.6, 0.6))

stars4 <- data.frame(Gender = as.factor("Male"), 
                    Condition="AI-Generated", 
                    label="***",
                    x=c(1),
                    y=c(0.545))

@@

p2 <- pred2 |> 
  ggplot(aes(x=Feedback_NoFacesAttractive, y=Predicted)) +
  geom_line(aes(color=Condition, group=Condition), linewidth=.3, position = position_dodge(width=0.4), key_glyph = "path") +
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.4), size=0.8, linewidth=1, key_glyph = "blank") +
  geom_text(data=stars3, aes(x=x, y=y, label=label, color=Condition), hjust=0.5, key_glyph = "blank", size=3) +
  geom_text(data=stars4, aes(x=x, y=y, label=label), hjust=0.5, color="#424242", size=3) +
  guides(color=guide_legend(override.aes = list(linewidth = 1.5))) +
  facet_grid(~Gender) +
  scale_y_continuous(labels=scales::percent) +
  scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 8),
        strip.placement = "outside",
        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
        strip.text.x = element_text(size = 10),
        strip.text.y = element_text(size = 10),
        axis.text.x = element_text(size=9, color="black"),
        legend.text = element_text(size = 10)) +
  labs(y="Realness\n", fill="Images presented as:", color="Images presented as:",
       x = "\n'No faces attractive' Feedback",
       tag = "B")

@@

p <- (p1 + theme(legend.position = "none")) / p2  + plot_layout(guides = "collect")
p
```
